RDF Validation of Metadata \\ on Highly-Complex Person-Level Data

### 2015-02-04 paper/paper7/paper7-appendix.tex
disco validation rules

\begin{abstract}

@@

@@

\textcolor{blue}{multiple validation levels}

Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.

We state one Disco constraint for each constraint type.

Constraint types marked with an asterisk can be used as an OWL 2 axiom.
Thus, reasoners may be used to infer implicit triples resolving constraint violations causing when these constraints are validated.
\textcolor{blue}{example}

>>>>

\begin{abstract}
...

@@

Bosch and Eckert initiated a comprehensive database\footnote{Publicly available at \url{http://purl.org/net/rdf-validation}.} on RDF validation requirements to collect case studies, use cases, and requirements \cite{BoschEckert2014}. 
It is continuously updated and used to evaluate and to compare various existing solutions for RDF constraint formulation and validation. 
Requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain.
Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages) \cite{BoschNolleAcarEckert2015}.

@@

We state at least one Disco constraint for the majority of the constraint types.
Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.
Constraint types marked with an asterisk can be used as OWL 2 axioms.
Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.

### 2015-02-04 paper/paper7/paper7.tex
disco validation rules

\textbf{RDF Data Cube Vocabulary.}
A well-formed RDF Data Cube is an a RDF graph describing one or more instances of {\em qb:DataSet} for which each of the defined integrity constraints passes.
Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more Data Cube instances which violate the corresponding constraint.
\cite{CyganiakReynolds2014}

>>>>

\textbf{RDF Data Cube Vocabulary.}
A well-formed RDF Data Cube is an a RDF graph describing one or more instances of {\em qb:DataSet} for which each of the defined integrity constraints passes.
Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more Data Cube instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
